\documentclass[a4paper,11pt]{article}

\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{url}

\usepackage{xcolor}
\newcommand{\bluenote}[1]{\color{blue}{ \em #1 }\color{black}}

\usepackage{geometry}
 \geometry{
 a4paper, %letterpaper,
 total={17cm,22.8cm},
 margin=24mm,
 top=22.4mm,
 bottom=25.4mm
 }
 
% Times new roman
\usepackage{mathptmx}

\usepackage[T1]{fontenc}

\thispagestyle{empty} 

\setlength{\parindent}{0pt}


\begin{document}

\date{}

\title{Draft Abstract}


\maketitle 

\section{Questions?}
\begin{itemize}
    \item Can a RL agent learn symbolically? 
    \item How can a safe controller \cite{vnc20} ensure the safe deployment of RL in the physical world [Safe set property]?
    \item Would a RL whose rewards are adapted to the safe sets given by the controller converge to the same safe sets? 
\end{itemize}

\section{What?}
\begin{itemize}
    \item Combining a car platooning safe controller w/ soft contraints and RL as to optimize the speed values that minimize the gap between vehicles
    \item Exploring different combinations: 
            \begin{itemize}
                \item Constraining actions given the controller constraints as to ensure that safety properties are respected [efficiency + structure algorithm]
                \item Adapt rewards given the controller constraints, as to investigate the convergence towards optimal policy [faster learning? can expect a crash before it happens?]
            \end{itemize}
    \item Controller to act as action governor of the RL agent.
\end{itemize}
\section{Why?}
\begin{itemize}
    \item From AI side: Importance of developing methods to make it acceptably safe to embed reinforcement learning controllers in
          a real life physical environment.
    \item From Controller side: Optimizing final values given in the range as to minimize gap. 
\end{itemize}

\section{How?}
\textcolor{red}{???????}

\bibliographystyle{unsrt}
\bibliography{biblio.bib}

\end{document}